Constraining the Interiors of Asteroids Through Close Encounters

### 2022-06-15 paper/main.tex
Added hybrid frame into computations

To extract a density distribution for the asteroid, we divide the asteroid into $N$ finite elements of uniform density. When the $K_{3m}$ are extracted, 16 moments are known. However, one of these is redundant with the mass of the asteroid, which must be fixed since density cannot be determined absolutely. Six more are redundant with the position and orientation of the coordinate axes, such that only nine finite elements are free. On all the $N$ densities, we place constraints that $0.25 < \rho < 3$, in units where the average density of the asteroid is one (i.e., the mass of the asteroid is set equal to the volume).

>>>>

To extract a density distribution for the asteroid, we divide the asteroid into $N$ finite elements of uniform density. When the $K_{3m}$ are extracted, 16 moments are known. However, one of these is redundant with the mass of the asteroid, which must be fixed since density cannot be determined absolutely. We set the asteroid mass equal to its volume, so that the average density is one and thus the extracted densities can be interpreted as ratios of $\rho / \rho_\text{avg}$.Three more are redundant with the center of mass, such that only twelve finite elements are free. In cases where $\gamma_0$ is known very accurately such that the correction imposed by equation \ref{eqn:body-fixed-to-hybrid} is very small, it is numerically favourable not to impose this equation on $K_{2m}$. In this case, the three orientation constraints that set $K_{21}=\Im K_{22} = 0$ carry over to the hybrid frame so that there are nine degrees of freedom. On all the $N$ densities, we place additional constraints that $0.25 < \rho < 3$.
